Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-04 ICPP-19/communications.tex
A new directoy with modified plots

	\todo[inline]{may convert 10 subplots to 8 in all performance diagrams}
	\todo[inline]{increase font size in all plots, may be free scale-y}
	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}

	We evaluate different data transfer heuristics for the several memory capacities. From the obtained traces, first we determine the minimum requirement of the memory capacity $m_c$ to execute all tasks. Then we observe the behavior of all heuristics with memory capacity  $m_c$ to $2m_c$, in the gap of $0.1m_c$. Our performance metric is $ratio\_to\_optimal$, which is defined as the following. Let the makespan of a heuristic $H$ is $M_H$ and the makespan of the optimal  case with infinite memory is $OMIM$, then  $ratio\_to\_optimal (H)$ is $\frac{M_H}{OMIM}$ (lower value is better). This value would be  greater or equal to $1$. A value closer to $1$ indicates that suitability of a particular heuristic and maximum possible communication-computation overlap has been achieved for that heuristic.

	Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} depict the distribution of the performance  of each heuristic for all considered memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
\subsection{HF Performance}	
	\begin{figure}[htb]
		\includegraphics[scale=0.3]{../ExperimentalResults/ratio_to_optimal_hf.pdf}
		\caption{Comparison of different heuristics for HF.}
		\label{fig:ratio_to_optimal_hf}
	\end{figure}
 As indicated above, HF tasks are highly homogeneous, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}. All heuristics depict similar behavior for minimum memory capacity $m_c$  and  increasing the memory capacity slightly does not change the performance of all heuristics. As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), static order with dynamic correction variants outperform others. \textit{Gilmore-Gomory} heuristic does not achieve good performance. it can be understand from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.

	\begin{figure}[htb]
	\includegraphics[scale=0.25]{../ExperimentalResults/inverse_ratio_to_optimal_hf-best.pdf}
	\caption{Comparision of best variants of all categories for HF.}
	\label{fig:ratio_to_optimal_best_hf}
	\end{figure}

@@

	\begin{figure}[htb]
	\includegraphics[scale=0.3]{../ExperimentalResults/ratio_to_optimal_ccsd.pdf}
	\caption{Comparison of different heuristics for CCSD.}
	\label{fig:ratio_to_optimal_ccsd}
	\end{figure}

@@

	\begin{figure}[htb]
	\includegraphics[scale=0.25]{../ExperimentalResults/inverse_ratio_to_optimal_ccsd-best.pdf}
	\caption{Comparision of best variants of all categories for CCSD.}
	\label{fig:ratio_to_optimal_best_ccsd}
	\end{figure}

@@

 \begin{figure}[htb]
 	%\begin{tabular}{c}
 	\subfloat[HF workloads\label{fig:hfProperties}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
 	}%\\
 	\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
 	}%\\
 	%\end{tabular}
	\caption{HF and CCSD tasks characteristics.}
    \label{fig:ApplicationProperties}
 \end{figure}

@@

	\begin{figure}[htb]
	\includegraphics[scale=0.25]{../ExperimentalResults/makespan_with_lp.pdf}
	\caption{Comparision of different heuristics with MILP solution based heuristic.}
	\label{fig:iterativeLpSolution}
\end{figure}

@@

 \begin{figure}[htb]
	\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
	}%\\
	\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
	}%\\
	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
	\label{fig:best_variants_batch}
 \end{figure}

@@

\subsection{Impact of heterogeneity on different heuristics}
\todo[inline]{SKumar: remove this subsection or replace with an experiment which shows the performance difference with all classes of heuristics for randomly generated inputs.}
	\begin{figure}[htb]
	\includegraphics[scale=0.3]{../ExperimentalResults/ccsd-random/ratio_to_optimal_ccsd_random.pdf}
	\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}
	\label{fig:ratio_to_optimal_ccsd_random}
	\end{figure}

@@

\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{article}

>>>>

%%	\todo[inline]{may convert 10 subplots to 8 in all performance diagrams}
	\todo[inline]{increase font size in all plots, may be free scale-y}
	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}

	We evaluate different data transfer heuristics for the several memory capacities. From the obtained traces, first we determine the minimum requirement of the memory capacity $m_c$ to execute all tasks. Then we observe the behavior of all heuristics with memory capacity  $m_c$ to $2m_c$, in the gap of $0.125m_c$. Our performance metric is $ratio\_to\_optimal$, which is defined as the following. Let the makespan of a heuristic $H$ is $M_H$ and the makespan of the optimal  case with infinite memory is $OMIM$, then  $ratio\_to\_optimal (H)$ is $\frac{M_H}{OMIM}$ (lower value is better). This value would be  greater or equal to $1$. A value closer to $1$ indicates that suitability of a particular heuristic and maximum possible communication-computation overlap has been achieved for that heuristic.

	Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} depict the distribution of the performance  of each heuristic for all considered memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
\subsection{HF Performance}	
	\begin{figure}[htb]
		\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_selected_hf.pdf}
		\caption{Comparison of different heuristics for HF.}
		\label{fig:ratio_to_optimal_hf}
	\end{figure}
 As indicated above, HF tasks are highly homogeneous, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}. All heuristics depict similar behavior for minimum memory capacity $m_c$  and  increasing the memory capacity slightly does not change the performance of all heuristics. As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), static order with dynamic correction variants outperform others. \textit{Gilmore-Gomory} heuristic does not achieve good performance. it can be understand from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.

	\begin{figure}[htb]
	\includegraphics[scale=0.225]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
	\caption{Comparision of best variants of all categories for HF.}
	\label{fig:ratio_to_optimal_best_hf}
	\end{figure}

@@

	\begin{figure}[htb]
	\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
	\caption{Comparison of different heuristics for CCSD.}
	\label{fig:ratio_to_optimal_ccsd}
	\end{figure}

@@

	\begin{figure}[htb]
	\includegraphics[scale=0.225]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
	\caption{Comparision of best variants of all categories for CCSD.}
	\label{fig:ratio_to_optimal_best_ccsd}
	\end{figure}

@@

 \begin{figure}[htb]
 	%\begin{tabular}{c}
 	\subfloat[HF workloads\label{fig:hfProperties}]{%
		\includegraphics[width=.45\linewidth]{./results/plots/application_properties_hf.pdf}
 	}%\\
 	\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
		\includegraphics[width=.45\linewidth]{./results/plots/application_properties_ccsd.pdf}
 	}%\\
 	%\end{tabular}
	\caption{HF and CCSD tasks characteristics.}
    \label{fig:ApplicationProperties}
 \end{figure}

@@

	\begin{figure}[htb]
	\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
	\caption{Comparision of different heuristics with MILP solution based heuristic.}
	\label{fig:iterativeLpSolution}
\end{figure}

@@

 \begin{figure}[htb]
	\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
		\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_hf_batch-best.pdf}
	}%\\
	\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
		\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
	}%\\
	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
	\label{fig:best_variants_batch}
 \end{figure}

@@

\subsection{Impact of heterogeneity on different heuristics}
\todo[inline]{SKumar: remove this subsection or replace with an experiment which shows the performance difference with all classes of heuristics for randomly generated inputs.}
	\begin{figure}[htb]
	\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_random_selected_ccsd.pdf}
	\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}
	\label{fig:ratio_to_optimal_ccsd_random}
	\end{figure}

@@

\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{communications}
